Evolving Dynamics: The U.S. Labor Force from 1972 to 2022

### 2024-03-16 paper/paper.qmd
updated data section

---
title: "Evolving Dynamics: The U.S. Labor Force from 1972 to 2022 and the Enduring Challenges for Women in the Workplace"
subtitle: "My subtitle if needed"
author: 
  - Michael Fang
  - Harrison Huang
  - David James Dimalanta
thanks: "Code and data are available at: https://github.com/fanger2791/fanger2791-Enduring-Challenges-for-Women-in-the-Workplace."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

variable_data <- data.frame( 
  Variable = c("fejobaff", 
               "fehire", 
               "Fefam",
               "Discaffw"), 
  Description = c("For or against preferential hiring of                       women",
                  "Should hire and promote women",
                  "Is it better for man to work, and a woman                    to tend home", 
                  "A woman won't get a job or promotion"), 
  ExampleResponse = c("Strongly Favor", 
              "Disagree", 
              "Agree",
              "Somewhat likely")
)
variable_data |>
 slice(1:10) |>
  kable(digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

@@

>>>>

---
title: "Evolving Dynamics: The U.S. Labor Force from 1972 to 2022"
subtitle: "The Enduring Challenges for Women in the Workplace"
author: 
  - Michael Fang
  - Harrison Huang
  - David James Dimalanta
thanks: "Code and data are available at: https://github.com/fanger2791/fanger2791-Enduring-Challenges-for-Women-in-the-Workplace."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

variable_data <- data.frame( 
  Variable = c("Fejobaff", 
               "Fehire", 
               "Fefam",
               "Discaffw"), 
  Description = c("For or against preferential hiring of                       women",
                  "Should hire and promote women",
                  "Is it better for man to work, and a woman                    to tend home", 
                  "A woman won't get a job or promotion"), 
  ExampleResponse = c("Strongly Favor", 
              "Disagree", 
              "Agree",
              "Somewhat likely")
)
variable_data |>
 slice(1:10) |>
  kable(digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

@@

R [@citeR] was the language and environment used for this paper as well as throughout the data cleaning process, with different packages such as tidyverse [@tidyverse], ggplot2 [@ggplot2], dplyr [@dplyr], tidyr [@tidyr], knitr [@knitr] packages.

From searching and filtering through different variables within the GSS, we were able to tabulate different datasets. Through this tabulation process, we were able to examine which years had data and years that did not, which allowed us to remove the empty years from the dataset.
